*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-29 Code/Manuscript_O2.Rmd

Three xenic cultures of *P. marinus* were obtained from Bigelow Labs, NCMA
Maine, US (REFERENCE). MED4 (CCMP1986) is from High-Light adapted (HLI) clade; SS120
(CCMP1375) is from Low-Light adapted (LLIII) clade; and MIT9313 (CCMP2773)
is from Low-Light adapted (LLIV) clade. Cultures were
maintained in incubators set to 22°C with a light/dark cycle of 12 h. The PAR level for maintenance cultures reflected Photosynthetically Active Radiation (PAR) in the source
niche of the ecotype; MED4, of 160 µmol photons m^-2^ s^-1^ with illumination from STANDARD Products Inc. Cool White F24T5/41K/8/HO/PS/G5/STD, 24 watts, fluorescent bulbs; SS120 and
MIT9313 at 30 µmol photons m^-2^ s^-1^ with illumination from Philips Cool White F14T5/841 Alto, 14 watts, fluorescent bulbs. To maintain active growth all strains were
transferred weekly with 1 in 5 dilution with Pro99 media
[@mooreCulturingMarineCyanobacterium2007] prepared with autoclaved artificial
seawater [@bergesEvolutionArtificialSeawater2001].

@@

Guided by the evidence of ocean distributions of proteins from *Prochlorococcus* we set up a matrix of photoperiods, PAR, spectral bands, and [O~2~] to approximate current, and potential future, latitudinal, depth and seasonal niches for *Prochlorococcus* strains.  We earlier found [@murphyPhotoinactivationPhotosystemII2017] that growth under red light could prove mechanistically informative as to factors limiting *Prochlorococcus* growth, so we included that spectral band even though it is not characteristic of representative *Prochlorococcus* niches.  Although *Prochlorococcus* is currently limited to a narrow range of surface photoperiods, potential poleward latitudinal expansions, in combination with attenuation of light with depth, mean *Prochlorococcus* currently, or potentially, encounters a wide range of photoperiods.  Our growth rate determinations generally agreed with those from @mooreComparativePhysiologySynechococcus1995, for white LED and 250 µM O~2~, but our study is, we believe, the first to analyze the interactive growth responses of *Prochlorococcus* strains to varying [O~2~], spectral wavebands and photoperiods.

>>>>

Three xenic cultures of *P. marinus* were obtained from Bigelow Labs, NCMA
Maine, US (REFERENCE). MED4 (CCMP1986) is from High-Light adapted (HLI) clade; SS120
(CCMP1375) is from Low-Light adapted (LLIII) clade; and MIT9313 (CCMP2773)
is from Low-Light adapted (LLIV) clade. Cultures were
maintained in incubators set to 22°C with a light/dark cycle of 12 h. The PAR level for maintenance cultures reflected Photosynthetically Active Radiation (PAR) in the source
niche of the ecotype; MED4, of 160 µmol photons m^-2^ s^-1^ with illumination from STANDARD Products Inc. Cool White F24T5/41K/8/HO/PS/G5/STD, 24 watts, fluorescent bulbs; SS120 and
MIT9313 at 30 µmol photons m^-2^ s^-1^ with illumination from Philips Cool White F14T5/841 Alto, 14 watts, fluorescent bulbs. To maintain active growth all strains were
transferred weekly with 1 in 5 dilutions with Pro99 media
[@mooreCulturingMarineCyanobacterium2007] prepared with autoclaved artificial
seawater [@bergesEvolutionArtificialSeawater2001].

@@

Guided by the evidence of ocean distributions of proteins from *Prochlorococcus* we set up a matrix of photoperiods, PAR, spectral bands, and [O~2~] to approximate current, and potential future, latitudinal, depth and seasonal niches for *Prochlorococcus* strains.  We earlier found [@murphyPhotoinactivationPhotosystemII2017] that growth under red light could prove mechanistically informative as to factors limiting *Prochlorococcus* growth, so we included that spectral band even though it is not characteristic of representative *Prochlorococcus* niches.  Although *Prochlorococcus* is currently limited to a narrow range of surface photoperiods, potential poleward latitudinal expansions, in combination with attenuation of light with depth, mean *Prochlorococcus* may potentially encounter a wide range of photoperiods.  Our growth rate determinations generally agreed with those from @mooreComparativePhysiologySynechococcus1995, for white LED and 250 µM O~2~, but our study is, we believe, the first to analyze the interactive growth responses of *Prochlorococcus* strains to varying [O~2~], spectral wavebands and photoperiods.
